Flexibility of interactions depends on habitat suitability

### 2019-07-01 paper/manuscript.Rmd
Correct typo of variable for number of cleaned names in msc

```{r}
loadd(spp_to_download, gbif_keys, n_occurrences)
n_species_with_occurrences <- dplyr::full_join(spp_to_download, gbif_keys, 
		 by = c("sp_name" = "queried_sp_name")) %>%
  dplyr::inner_join(n_occurrences, by = c("key" = "taxonKey")) %$% 
  dplyr::n_distinct(sp_id)

n_species_with_clean_occurrences <-  dplyr::full_join(spp_to_download, gbif_keys, 
		 by = c("sp_name" = "queried_sp_name")) %>%
  dplyr::inner_join(n_cleaned_occurrences, by = c("key" = "taxonKey")) %$% 
  dplyr::n_distinct(sp_id)

@@

Our next step was to determine the habitat suitability of the species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
To do that we first fit a climatic envelope for each  of them which requires information about the climate and their known occurrences. 
We retrieved occurrences from the Global Biodiversity Information Facility (https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
We only requested occurrences that had geolocation information and no known geospatial issue.
This resulted into roughly `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for `r format(n_species_with_occurrences, big.mark = ",")` species.
We were unable to find occurrences for the remaining `r dplyr::n_distinct(spp_to_download$sp_id) - n_species_with_occurrences` species. 
We then filtered these occurrence and kept only those with higher quality information. 
Specifically, we removed occurrences with a coordinate uncertainity larger than 100km and those recorded prior to 1945 (Audrey: ref? or why?).
We also removed occurrences in which the number of individuals recorded was zero or more than 100 as such large counts are often erroneous (Audrey: ref? or why?). 
We only kept occurrence records describing a human observation and preserved specimens as they are more reliable (Audrey: ref?why?). 
After these filtering, we used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] to further identify (*i*) coordinates outside the borders of the country in which they were recorde, (*ii*) those arround a the country capital or the centroid of the country and province centroids, (*iii*) those arond a biodiversity institution, and (*iv*) those located within oceans. 
We used land and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale. 
This resulted in `r round(sum(n_cleaned_occurrences$N)/1000000, digits = 1)` million occurrences for `r n_species_with_cleaned_occurences` species.

>>>>

```{r}
loadd(spp_to_download, gbif_keys, n_occurrences, n_cleaned_occurrences)
n_species_with_occurrences <- dplyr::full_join(spp_to_download, gbif_keys, 
		 by = c("sp_name" = "queried_sp_name")) %>%
  dplyr::inner_join(n_occurrences, by = c("key" = "taxonKey")) %$% 
  dplyr::n_distinct(sp_id)

n_species_with_cleaned_occurrences <-  dplyr::full_join(spp_to_download, gbif_keys, 
		 by = c("sp_name" = "queried_sp_name")) %>%
  dplyr::inner_join(n_cleaned_occurrences, by = c("key" = "taxonKey")) %$% 
  dplyr::n_distinct(sp_id)

@@

Our next step was to determine the habitat suitability of the species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
When organims were identified to the subspecies or varieties, we , 
To do that we first fit a climatic envelope for each  of them which requires information about the climate and their known occurrences. 
We retrieved occurrences from the Global Biodiversity Information Facility (https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
We only requested occurrences that had geolocation information and no known geospatial issue.
This resulted into roughly `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for `r format(n_species_with_occurrences, big.mark = ",")` species.
We were unable to find occurrences for the remaining `r dplyr::n_distinct(spp_to_download$sp_id) - n_species_with_occurrences` species. 
We then filtered these occurrence and kept only those with higher quality information. 
Specifically, we removed occurrences with a coordinate uncertainity larger than 100km and those recorded prior to 1945 (Audrey: ref? or why?).
We also removed occurrences in which the number of individuals recorded was zero or more than 100 as such large counts are often erroneous (Audrey: ref? or why?). 
We only kept occurrence records describing a human observation and preserved specimens as they are more reliable (Audrey: ref?why?). 
After these filtering, we used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] to further identify (*i*) coordinates outside the borders of the country in which they were recorde, (*ii*) those arround a the country capital or the centroid of the country and province centroids, (*iii*) those arond a biodiversity institution, and (*iv*) those located within oceans. 
We used land and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale. 
This resulted in `r round(sum(n_cleaned_occurrences$N)/1000000, digits = 1)` million occurrences for `r n_species_with_cleaned_occurrences` species.
